---
title: "Visualize Data"
author: "Mackenzie Eckles"
format: gfm
execute: 
  echo: true
  eval: true
---


<!-- If you get the error "Error in list2(na.rm = na.rm, ...) : object 'ffi_list2' not found" do the following in the Console run:  

    remove.packages("rlang")

Then Restart R to be safe. Then run:

    install.packages("rlang")

and again restart R to be safe. That should fix the problem (which is a package dependency issue).   -->



Try your code again
```{r}
#| label: setup
#| include: false
library(tidyverse)
library(rlang)
```



## Your Turn 0

Add a setup chunk that loads the tidyverse packages.


```{r}
#| label: Adding-data
head(mpg)
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}
#| label: Making-a-graph
# creating a scatterplot
ggplot(mpg) +
  geom_point(aes(x = displ, 
                 y = hwy))
```


## Your Turn 2

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
#| label: Creating-a-Boxplot
# altering code to make a boxplot
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = class, y = hwy))
```


## Your Turn 3

Make a histogram of the `hwy` variable from `mpg`. Hint: do not supply a y variable.

```{r}
#| label: Creating-a-histogram
# Make a histogram

ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = hwy))
```

## Your Turn 4

Use the help page for `geom_histogram` to make the bins 2 units wide.

```{r}
#| label: Changing-Bin-Width
# Make bins 2 units wide
ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = hwy), binwidth = 2)
```


## Your Turn 5

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
#| label: Change-Graph-Aesthetics
# add color, size, alpha, and shape

ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, 
                           y = hwy),
             color = "magenta",
             size = 2,
             alpha = 0.5,
             shape = "square")
```

## Help Me

What do `facet_grid()` and `facet_wrap()` do? 
(run the code, interpret, convince your group)

```{r}
#| label: Using-Facets
# Makes a plot that the commands below will modify
q <- ggplot(mpg) + geom_point(aes(x = displ, y = hwy))

q + facet_grid(. ~ cyl)
q + facet_grid(drv ~ .)
q + facet_grid(drv ~ cyl)
q + facet_wrap(~ class)
```


## Your Turn 6

Make a bar chart `class` colored by `class`. Use the help page for `geom_bar` to choose a "color" aesthetic for class.

```{r}
#| label: Making-a-Barchart
# fill for bars

ggplot(data = mpg) +
  geom_bar(mapping = aes(x = class, fill = class)) +
  guides(fill = "none")+
  labs(x = "Class of Vehicle",
       y = "Number of Vehicles in Sample")+
  theme_classic()
```

## Quiz

What will this code do?

This will add multiple geometries to the same plot.

```{r}
#| label: Multiple-Geometries

ggplot(mpg) + 
  geom_point(aes(displ, hwy)) +
  geom_smooth(aes(displ, hwy)) 
# saving graphs:
# ggsave("example.jpg", width = _, height = _)
```


***

# Take aways

You can use this starter code template to make thousands of graphs with **ggplot2**.

```{r}
#| label: template
#| eval: false
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```